Target Markdown

### 2023-05-17 _targets.Rmd
small updates and improvements

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs"
                            ))

@@

```{targets article}
list(
    # tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
)

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych"
                            ))

@@

```{targets article}
list(

    # tar_target(results,
    #            analyse(full_indicator),
    #            format = "qs") ,
    # tar_target(sup_testing,
    #            sup_test(matching, db_path, ids, sup_control, ids_complete),
    #            format = "qs") ,
    # 
    # tarchetypes::tar_render(article, here::here("Rmd", "article.Rmd"))
)
